---
title: "Server Admin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Server Admin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contains functions for administering a local Neo4J server.

### Start, stop, restart or check the status of a local Neo4J server

`neo4J_start()`, `neo4j_stop()`, `neo4j_restart()` and `neo4j_status()` perform a stop, start, restart or reports the current status of a local Neo4J instance.  These functions take a single argument `neo4j_path` which should be a path to the local `neo4j` executable.  Use `path.expand()` where necessary.

```{r example, eval = FALSE}
library(neo4jshell)

neo_path <- path.expand("~/neo4j-community-4.0.4/bin/neo4j")
neo4j_status(neo_path)
```

All these functions output system messages.

### Wipe a specified graph from a local Neo4J server

`neo4j_wipe()` completely removes a graph from the local Neo4J server.  It takes two arguments:

* `database` is the name of the graph database file to be wiped.
* `data_path` is the path to the data directory of the local Neo4J server.  Use `path.expand()` if necessary.

``` {r example2, eval = FALSE}
graphfile <- "graph.db"
my_data_path <- path.expand("~/neo4j-community-4.0.4/data")
neo4j_wipe(graphfile, my_data_path)

```

This function will output a success or an error message.

### Note for Windows users

Paths to executable files that are provided as arguments to functions may need to be provided with appropriate extensions (eg `neo4j.bat`).
